Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-09-08 manuscript/manuscript.tex
drafted discussion

@@

@@

>>>>

%% float control
\renewcommand\floatpagefraction{0.75}
% \renewcommand\topfraction{.8}
% \renewcommand\bottomfraction{.8}
% \renewcommand\textfraction{.2}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

@@

\jy{The 'title' in each figure could be removed because we have
  captions. The fonts of the annotations in the figures need to be
  increased. The code generating them need to be tidied for future
  sharing.
}

@@

Our study highlights the vital importance of robust data curation in
maintaining the reliability and utility of open datasets, with a close
examination of the NYC 311 data. As these datasets are applied across
diverse fields such as public services and academic research, issues
like inconsistencies, missing values, and formatting errors can
significantly undermine the quality of insights. Trustworthy machine
learning systems, which rely heavily on high-quality data, are
particularly vulnerable to errors when data is not properly
curated. For example, biases or inconsistencies in input data can
compromise both the accuracy and fairness of predictive models
\citep{rahm2000data}.

This research further emphasizes the necessity of harmonizing data
from multiple city agencies, particularly in resolving discrepancies
in field names, formats, and definitions. Trustworthy machine learning
depends on not only accurate and clean data but also consistent data
across sources. This challenge becomes more acute in datasets spanning
long time periods, where changes in agency structures or reporting
standards can introduce subtle biases. As \citet{rahm2000data} noted,
ensuring long-term data consistency is crucial for longitudinal
studies and predictive modeling, as even minor shifts in data can
result in significant deviations in outcomes.

Finally, the intersection of data curation and machine learning for
public policy applications opens new opportunities for enhancing
governance. By improving data quality, machine learning models can
more effectively predict trends, allocate resources, and identify
issues such as service delays. The COVID-19 pandemic demonstrated the
critical role of real-time, trustworthy data in responding to public
needs. Without proper data curation, the accuracy and timeliness of
machine learning insights would have been compromised, affecting
crucial decision-making processes. Future efforts could focus on
automating data curation within real-time data pipelines, ensuring
that the data feeding into machine learning models remains both clean
and reliable \citep{chu2016data}.
